---
title: "ENVS 193DS - Homework 3"
author: "Izzy Chang"
date: "2025-05-23"
format: html
---

## GitHub Repository:

<https://github.com/izzy-chang/ENVS-193DS_homework-03>

## Set Up

```{r}
#| message: false

# setting up packages
library(tidyverse)
library(here)
library(janitor)
library(readxl)
library(gt)
```

## Problem 1. Personal data

### a. Data summarizing

\[I calculated the mean time spent working on my thesis (in hours) for each type of caffeine I consume that day. This is informative because different types of caffeine may affect my focus and productivity, which could influence how much time I am able to spend on my thesis.\]

### b. Visualization

```{r - data visualization}

# reading in data file and storing as an object named "my_data"
my_data <- read_csv(here("data", "personal_data.csv")) 

summary_thesis <- my_data |> 
  group_by(Caffeine_Consumed) |> 
  summarize(mean_thesis_time = mean(Thesis_Time_hrs))

ggplot(my_data, aes(
  x = Caffeine_Consumed,
  y = Thesis_Time_hrs,
  fill = Caffeine_Consumed
)) + 
  geom_jitter(width = 0.2, alpha = 0.5) + 
  stat_summary(fun = mean, geom = "bar", color = "black", alpha = 0.7, width = 0.6) + 
  scale_fill_manual(values = c("Coffee" = "darkmagenta", "Decaf Coffee" = "darkorange", "Matcha" = "darkgreen", "None" = "darkblue")) + 
  labs(
    title = "Average Time Spent of Thesis by Caffeine Type",
    x = "Caffeine Type",
    y = "Thesis Time (hours)"
  )
```

### c. Caption

**\[Figure 1.** Mean time spent working on my thesis by type of caffeine consumed. Each dot represents one day's recorded thesis work time. Bars indicate the average thesis time for each caffeine category.\]

### d. Table presentation

```{r}
summary_thesis |> 
  mutate(mean_thesis_time = round(mean_thesis_time, 1)) |> 
  gt() |> 
  tab_header(
    title = "Mean Thesis Time by Caffeine Type"
  ) |> 
  cols_label(
    Caffeine_Consumed = "Caffeine Type",
    mean_thesis_time = "Mean Thesis Time (hours)"
  )
```

## Problem 2. Affective visualization

### a. Describe in words what an affective visualization could look like for your personal data

\[I could make a scatter pot with phone screen time on the x-axis and time spent on my thesis on the y-axis to see how these two variables relate. Each point would present a day, and I could use different colors or shapes to indicate the type of caffeine consumed that day. For extra insight, the size of the points could reflect the number of classes I had that day, showing how my schedule might influence both screen and thesis time. This visualization would help me quickly identify patterns or correlations, like whether high screen time is linked to less thesis work or if caffeine impacts this relationship.\]

### b. Create a sketch (on paper) of your idea

\[\]

### c. Make a draft of your visualization

\[\]

### d. Write an artist statement

\[\]

## Problem 3. Statistical critique

### a. Revisit and summarize

### b. Visual clarity

### c. Aesthetic clarity

### d. Recommendations
