---
title: "ENVS 193DS - Homework 3"
author: "Izzy Chang"
date: "2025-05-23"
format: html
---

## GitHub Repository:

<https://github.com/izzy-chang/ENVS-193DS_homework-03>

## Set Up

```{r}
#| message: false

# setting up packages
library(tidyverse)
library(here)
library(janitor)
library(readxl)
library(gt)
```

## Problem 1. Personal data

### a. Data summarizing

\[I could calculate the mean number of thesis hours I worked to compare average thesis productivity between days with above-median and below-median screen time, because I think I tend to procrastinate more on high screen time days, which may reduce the time I spend on my thesis. I could divide my screen time data into high vs low screen time groups by using the median screen time.\]

### b. Visualization

```{r - data visualization}

# reading in data file and storing as an object named "my_data"
my_data <- read_csv(here("data", "personal_data.csv")) 

# convert Screen_Time_hrs to numeric
my_data <- my_data %>%
  mutate(Screen_Time_hrs = as.numeric(Screen_Time_hrs))

# create screen time groups based on the median
median_screen <- median(my_data$Screen_Time_hrs, na.rm = TRUE)

my_data <- my_data %>%
  mutate(Screen_Time_Group = if_else(Screen_Time_hrs > median_screen,
"High Screen Time", "Low Screen Time"))

# plot: thesis time by screen time group
ggplot(my_data, aes(x = Screen_Time_Group, y = Thesis_Time_hrs, fill = Screen_Time_Group)) + 
  geom_jitter(width = 0.2, alpha = 0.6, color = "gray") + 
  stat_summary(fun = mean, geom = "bar", width = 0.5, color = "black", show.legend = FALSE) + 
  scale_fill_manual(values = c("High Screen Time" = "coral", "Low Screen Time" = "lightblue")) +
  labs(
    title = "Thesis Time by Screen Time Group",
    x = "Screen Time Group",
    y = "Thesis Work Time (hours)"
  ) + 
  theme_minimal() +
  theme(legend.position = "none")
```

### c. Caption

### d. Table presentation

## Problem 2. Affective visualization

### a. Describe in words what an affective visualization could look like for your personal data

### b. Create a sketch (on paper) of your idea

### c. Make a draft of your visualization

### d. Write an artist statement

## Problem 3. Statistical critique

### a. Revisit and summarize

### b. Visual clarity

### c. Aesthetic clarity

### d. Recommendations

```         
```

```         
```
