---
title: "ENVS 193DS - Homework 3"
author: "Izzy Chang"
date: "2025-05-23"
format: html
---

## GitHub Repository:

<https://github.com/izzy-chang/ENVS-193DS_homework-03>

## Set Up

```{r}
#| message: false

# setting up packages
library(tidyverse)
library(here)
library(janitor)
library(readxl)
library(gt)
```

## Problem 1. Personal data

### a. Data summarizing

\[I calculated the mean time spent working on my thesis (in hours) for each type of caffeine I consume that day. This is informative because different types of caffeine may affect my focus and productivity, which could influence how much time I am able to spend on my thesis.\]

### b. Visualization

```{r - data visualization}

# reading in data file and storing as an object named "my_data"
my_data <- read_csv(here("data", "personal_data.csv")) 

# convert Screen_Time_hrs to numeric
my_data <- my_data %>%
  mutate(Screen_Time_hrs = as.numeric(Screen_Time_hrs))

# create screen time groups based on the median
median_screen <- median(my_data$Screen_Time_hrs, na.rm = TRUE)

my_data <- my_data %>%
  mutate(Screen_Time_Group = if_else(Screen_Time_hrs > median_screen,
"High Screen Time", "Low Screen Time"))

# plot: thesis time by screen time group
ggplot(my_data, aes(x = Screen_Time_Group, y = Thesis_Time_hrs, fill = Screen_Time_Group)) + 
  geom_jitter(width = 0.2, alpha = 0.6, color = "gray") + 
  stat_summary(fun = mean, geom = "bar", width = 0.5, color = "black", show.legend = FALSE) + 
  scale_fill_manual(values = c("High Screen Time" = "coral", "Low Screen Time" = "lightblue")) +
  labs(
    title = "Thesis Time by Screen Time Group",
    x = "Screen Time Group",
    y = "Thesis Work Time (hours)"
  ) + 
  theme_minimal() +
  theme(legend.position = "none")
```

### c. Caption

**\[Figure 1.** Comparison of thesis work time (in hours) between high and low screen time days. Each point represents a day's thesis hours, and the bar shows the mean thesis time for each group. Days with screen time above the median are labeled "High Screen Time," while those below the median are labeled "Low Screen Time." This figure illustrates how thesis productivity may vary based on daily screen usage.\]

### d. Table presentation

## Problem 2. Affective visualization

### a. Describe in words what an affective visualization could look like for your personal data

### b. Create a sketch (on paper) of your idea

### c. Make a draft of your visualization

### d. Write an artist statement

## Problem 3. Statistical critique

### a. Revisit and summarize

### b. Visual clarity

### c. Aesthetic clarity

### d. Recommendations
